---
title: "TIF Zip overlay"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Loading the Libraries
```{r}
library(ggplot2)
library(ggmap)
library(maps)
library(mapdata)
library(rgdal)
library(sf)
library(tidyverse)
library(rgeos)
library(rstudioapi)
library(tidyr)
library(broom)
library(RSocrata)
library(mapproj)
library(readxl)
library(scales)
```

Setting up the Chicago google map
```{r}
register_google(key = "AIzaSyDYu3ooTegFHilgtg0SnM8Iw2ggry1-kQI")
Chimap = map = get_map(location = 'Chicago', zoom = 11)
ggmap(Chimap)
```


Reading in shapefile for median income by zip
```{r}
chi_median_zip <- readOGR( 
  dsn= "/Users/andresmeza/Desktop/Boundaries_Zipcodes/" , 
  layer="income_zip")
names(chi_median_zip)
chi_median_zip$zip
```

Making shapefile into dataframe
```{r}
chi_zip_df <- spTransform(chi_median_zip, CRS("+proj=longlat +datum=WGS84"))
chi_zip_df.f = chi_zip_df %>% fortify(region = 'zip')
Chizips  = merge(chi_zip_df.f, chi_zip_df@data, by.x = 'id', by.y = 'zip')
Zips = Chizips %>% select(id) %>% distinct()
values = data.frame(id = c(Zips),
                      value = c(runif(Zips %>% count() %>% unlist(),5.0, 25.0)))
CHIzipfinal = merge(Chizips, values, by.x='id')
CHIzipfinal %>% group_by(id) %>% do(head(., 1)) %>% head(10)
```

Exporting shapefile dataframe as csv
```{r}
write.csv(CHIzipfinal, "/Users/andresmeza/Desktop/Boundaries_Zipcodes.csv")
```

Importing shapefile dataframe with associated median incomes
```{r}
names(Zips_income)
Zip_final <- cbind(CHIzipfinal, Zips_income[,13, drop=FALSE])
view(Zip_final)
```

Basic map of shapefile for zipcodes
```{r}
ggplot(CHIzipfinal, aes(long, lat, group = group)) +
    geom_polygon(aes(fill = value))
```

Basic Heatmap of zipcode shapefile with associated incomes
```{r}
ggplot(Zip_final, aes(long, lat, group = group)) +
    geom_polygon(aes(fill = medianincome))
```

Heatmap of income with google overlay
```{r}
ggmap(Chimap) +
    geom_polygon(aes(fill = medianincome, x = long, y = lat, group = group),
                 data = Zip_final,
                 alpha = 0.8,
                 color = "black",
                 size = 0.2)+labs(fill="Median Income")
```

Important TIF shapefile
```{r}
X2021_TIF_Report <- read_excel("2021 TIF Report.xlsx", 
    col_types = c("text", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "text"))
TIF_2021_df <- readOGR( 
  dsn= "/Users/andresmeza/Desktop/TIF_Boundaries/" , 
  layer="TIF_Boundaries")
TIF_districts <- spTransform(TIF_2021_df, CRS("+proj=longlat +datum=WGS84"))
TIF_districts.f = TIF_districts %>% fortify(region = 'name')
ChiTIFs  = merge(TIF_districts.f, TIF_districts@data, by.x = 'id', by.y = 'name')
TIFs = ChiTIFs %>% select(id) %>% distinct()
values = data.frame(id = c(TIFs),
                      value = c(runif(TIFs %>% count() %>% unlist(),5.0, 25.0)))
TIFfinal = merge(ChiTIFs, values, by.x='id')
TIFfinal %>% group_by(id) %>% do(head(., 1)) %>% head(10)
TIFfinal3 <- cbind(TIFfinal, TIFfinal2[,30, drop=FALSE])
colnames(TIFfinal3) [29] = "Propertytaxextraction"
```

Using TIF property extraction as size class in points
```{r}
ggplot(data = TIFfinal3) + 
geom_point(data=TIFfinal3, aes(long, lat, size="Propertytaxextraction"), inherit.aes = FALSE, alpha = 0.5, size = 0.5,color="red") + coord_equal()
```

Shapefile of TIF districts with associated proptaxextraction
```{r}
ggmap(Chimap) +
    geom_polygon(aes(fill = Propertytaxextraction, x = long, y = lat, group = group),
                 data = TIFfinal3,
                 alpha = 0.8,
                 size = 0.2) +
scale_fill_gradient(low = "blue", high = "red", name = "Property Tax Extraction", labels = comma) + 
  ggtitle("TIF Districts 2022") 
```
Side by side heatmaps of Proper tax extraction and median income
```{r}
ggmap(Chimap) +
    geom_polygon(aes(fill = Propertytaxextraction, x = long, y = lat, group = group),
                 data = TIFfinal3,
                 alpha = 0.8,
                 size = 0.2) +
scale_fill_gradient(low = "blue", high = "red", name = "Property Tax Extraction ($)", labels = comma) + 
  ggtitle("TIF Districts 2022") 
ggmap(Chimap) +
    geom_polygon(aes(fill = medianincome, x = long, y = lat, group = group),
                 data = Zip_final,
                 alpha = 0.8,
                 size = 0.2)+labs(fill="Median Income") +
scale_fill_gradient(low = "blue", high = "red", name = "Median Income ($)", labels = comma) + 
  ggtitle("TIF Districts 2022")
```


Attempt to overlay final maps
```{r}
ggmap(Chimap) +
    geom_polygon(aes(fill = medianincome, x = long, y = lat, group = group),
                 data = Zip_final,
                 alpha = 0.8,
                 color = "black",
                 size = 0.2) +
geom_point(data=TIFfinal3, aes(long, lat, size="Propertytaxextraction"), inherit.aes = FALSE, alpha = 0.1, size = 0.5,color="red") + coord_equal()+
  labs(fill="Median Income")
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.